---
title: "R4scSHARP"
author: "W-Holtz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{R4scSHARP}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# R4scSHARP

## Purpose:

The purpose of this document is primarily to get users acquainted with the tool R4scSHARP. One should not that this tool is not the primary functionality for the scSHARP project. Instead this is a component tool that will, in an ideal world, run primarily through the use of the python tool. If however, one would like to learn run this component separately, this is the vignette for them!

## Setup

To setup, one must first install and load the package. More details on installation can be found on the GitHub repository here: https://github.com/W-Holtz/R4scSHARP#installation

```{r}
library(R4scSHARP)
```

## Basics

Lets run through a simple example with the tool.

First let's setup our input variables.

```{r}
data_path <- "query_counts.csv.gz"
marker_path <- "markers.txt"
ref_path <- "ref_counts.csv.gz"
ref_label_path <- "ref_labels.csv"

```

The above variables are all of the required input parameters, but there are more parameters at our disposal then just paths:

-   out_path: Path represented as a string to desired location for the results to be saved. If no out_path parameter is given, no output file will be generated.
-   tools:  Tools you would like to run (runs all five tools by default). Example Inputs: "scina,scpred,singler", "sctype", or "scsorter"
-   min_cells:  Filters data so cells with a sample size less then the given amount are ignored (value is 0 by default)
-   min_feats:  Filters data so features with a sample size less then the given amount are ignored (value is 0 by default)


To run the tools, call the function:

```{r, include = FALSE}
output <- run_r4scsharp(data_path, marker_path, ref_path,
    ref_label_path)
```

```{r}
# prints the first five columns
print(head(output, 5))
```

The function returns the predictions from each tool as a data frame object in R if you'd like to print it out or play around with it more. It also will save the output to your given "out_path".
